new_analses

### 2021-07-20 Frontiers/Frontiers.Rmd
jhjh

---
title: "Adaptation of Palmer amaranth to the upper Midwest"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Maxwel C Oliveira
    affiliation: '1'
    etal: Oliveira # First author's last name. 
  - name: Amit J Jhala
    affiliation: '2'
  - name: Mark Bernards
    affiliation: '3'
  - name: Chris Proctor
    affiliation: '2'
  - name: Strahinja Stepanovic
    affiliation: '2'
  - name: Rodrigo Werle
    affiliation: '1'
    email: rwerle@uwisc.edu # Indicates corresponding Author
    institution: Department of Agronomy, University of Wisconsin-Madison, United States
    street: 1575 Linden Dr
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    zip: 53705
    country: United States
affiliation:
  - id: '1'
    department: Department of Agronomy
    institution: University of Wisconsin-Madison
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    country: United States
  - id: '2' 
    department: Department of Agronomy and Horticulture
    institution: University of Nebraska-Lincoln
    city: Lincoln
    state: Nebraska # only USA, Australia, Canada
    country: United States
  - id: '3' 
    department: Department of Agronomy
    institution: Western Illinois University
    city: Macomb
    state: Illnois # only USA, Australia, Canada
    country: United States
output: rticles::frontiers_article
csl: frontiers.csl
bibliography: adaptation.bib
---

@@

kgghkg

@@

```{r fig1, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../weather/Figure 1.png")
```

```{r fig2, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../june.png")
```

@@

```{r, Figure-2, ref.label = "fig2", echo = FALSE, message = FALSE, fig.height=3, fig.width=6, fig.align='center', fig.cap='Figure caption', out.width = "160mm", out.height = "90mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

>>>>

---
title: "Adaptation of Palmer amaranth to croppins systems"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Maxwel C Oliveira
    affiliation: '1'
    etal: Oliveira # First author's last name. 
  - name: Amit J Jhala
    affiliation: '2'
  - name: Mark Bernards
    affiliation: '3'
  - name: Chris Proctor
    affiliation: '2'
  - name: Strahinja Stepanovic
    affiliation: '2'
  - name: Rodrigo Werle
    affiliation: '1'
    email: rwerle@uwisc.edu # Indicates corresponding Author
    institution: Department of Agronomy, University of Wisconsin-Madison, United States
    street: 1575 Linden Dr
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    zip: 53705
    country: United States
affiliation:
  - id: '1'
    department: Department of Agronomy
    institution: University of Wisconsin-Madison
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    country: United States
  - id: '2' 
    department: Department of Agronomy and Horticulture
    institution: University of Nebraska-Lincoln
    city: Lincoln
    state: Nebraska # only USA, Australia, Canada
    country: United States
  - id: '3' 
    department: Department of Agronomy
    institution: Western Illinois University
    city: Macomb
    state: Illnois # only USA, Australia, Canada
    country: United States
output: rticles::frontiers_article
csl: frontiers.csl
bibliography: adaptation.bib
---

@@

Palmer amaranth (*Amaranthus palmeri* S. Watson) is an annual forb native to southwestern United States and northern Mexico. The species is a fast growing C4 species, XXX reported that Palmer amaranth can grow a inch per day. Palmer amaranth reproduce by dioecious plants outcrossing, a single plant can produce up to a million seeds.. Palmer amaranth as well as other Amaranthaceae species have been reported as an edible plant but it has become a concern to agriculture. The species is currently considered one of the most problematic weed species to US cropping systems.

 family. It is a dioecious species that can reach up to 3 m tall and produce a million seed per plant.

The species biology in combination to human intervention in agriculture made Palmer amaranth one of the most difficult species to control in the United States. Weed control in US agriculture is heavily based on herbicides. Palmer amaranth has showed a remarkable capacity to evolve resistance to herbicides. Thus far, Palmer amaranth has evolved resistance to X herbicide sites of action, which increases control complexity. Palmer amaranth is widespread to southern United States and it is currently moving to northern states. The increase movement of Palmer amaranth to US Midwest warrants investigation on species adaptation to that environment. Most studies are based on reactive but not in the proactive management.

The Palmer amaranth biology combined to human intervention in agriculture

 Palmer amaranth troublesomeness

The objective of this study was to investigate the flowering pattern, biomass, and height of Palmer amaranth growing under different environments and timing across five locations in the US Midwest.

@@

```{r fig1, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/weather/Figure 1.png")
```

```{r fig2, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/combine 3.png")
```

@@

```{r, Figure-2, ref.label = "fig2", echo = FALSE, message = FALSE, fig.height=9, fig.width=4, fig.align='center', fig.cap='Figure caption', out.width = "150mm", out.height = "260mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

### 2021-07-20 Frontiers/Frontiers.tex
jhjh

\title[Short Title]{Adaptation of Palmer amaranth to the upper Midwest}
\author[\firstAuthorLast]{\Authors}
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

@@

kgghkg

@@

{\centering \includegraphics[width=160mm,height=100mm]{../weather/Figure 1}

@@

{\centering \includegraphics[width=160mm,height=90mm]{../june}

>>>>

\title[Short Title]{Adaptation of Palmer amaranth to croppins systems}
\author[\firstAuthorLast]{\Authors}
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

@@

Palmer amaranth (\emph{Amaranthus palmeri}) is an indigenous species
from southwestern United States and northern Mexico. Palmer amaranth is
a C4 annual broadleaf forb within the \textbf{Amarantacea} family.
Palmer amaranth is currently considered one of the most troublesome weed
species in the United States.

@@

{\centering \includegraphics[width=160mm,height=100mm]{../data analysis/weather/Figure 1}

@@

{\centering \includegraphics[width=150mm,height=260mm]{../data analysis/figures/combine 3}

### 2021-07-20 data analysis/new_analyses.Rmd
jhjh

```{r}
data1 %>% 
  mutate(month = fct_recode(month,
                            "First transplanting" = "June",
                            "Second transplanting" = "July")) -> data1
```
```{r}
data1 %>% 
  filter(!is.na(weight)) %>% 
  group_by(year, location, month, crop) %>% 
  mutate(n = n()) %>% 
  mutate(biomass = weight / n) -> biom
```
```{r}
biom %>% 
  ggplot(aes(x = log(biomass))) + 
  geom_histogram()
```

>>>>

```{r}
data1 %>% 
  mutate(month = fct_recode(month,
                            "First transplanting" = "June",
                            "Second transplanting" = "July")) -> data1
```

```{r}
data1 %>% 
  filter(!is.na(weight)) %>% 
  group_by(year, location, month, crop) %>% 
  mutate(n = n()) %>% 
  mutate(biomass = weight / n) -> biom
```

```{r}
biom %>% 
  ggplot(aes(x = log(biomass))) + 
  geom_histogram()
```
